### 2019-03-21 Rapport/TG_ITA/Bibliographic_analysis/Coursera.tex
Assignment Week 2 Coursera
Linear Regression. Single and multivariables.

\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{Coursera}
\subsubsection{Week 1}
Machine Learning algorithms :
	Supervised learning
	Unsupervised learning
	Reinforcement Learning
	Recommender systems

Supervised Learning
	based on right answers
	Regression problem: predict continuous valued output (price)
	Classification problem: output value of 0 or 1
	%% COURSERA TEXT
	To describe the supervised learning problem slightly more formally, our goal is, given a training set, to learn a function h : X → Y so that h(x) is a “good” predictor for the corresponding value of y. For historical reasons, this function h is called a hypothesis. Seen pictorially, the process is therefore like this:
%%%%

@@

>>>>

\documentclass[12pt,a4paper]{report}
\newcommand{\dd}[1]{\mathrm{d}#1}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{Coursera}
\subsubsection{Week 1}
Machine Learning algorithms :
	Supervised learning
	Unsupervised learning
	Reinforcement Learning
	Recommender systems

Supervised Learning
	based on right answers
	Regression problem: predict continuous valued output (price)
	Classification problem: output value of 0 or 1
	%% COURSERA TEXT
	To describe the supervised learning problem slightly more formally, our goal is, given a training set, to learn a function h : X -> Y so that h(x) is a good predictor for the corresponding value of y. For historical reasons, this function h is called a hypothesis. Seen pictorially, the process is therefore like this:
%%%%

@@

Gradient descent Algorithm
	Optimize parameters in hypothesis function to minimize the cost function
	Convex functions has only a global optima, no local optima (good for working with)
	"Batch" gradient descent: each step of gradient descent uses all the training examples

Learning rate
	Controls how big the step is in the optimization process

\subsubsection{Week 2}
Fix a notation thorughout the work
	m -> the number of training examples i
	n -> the number of features j\\
	$ x^{(i)}_{j} $\\
	$ i = 1,...,m $\\
	$ j = 0,...,n $
	i are the lines and j the columns.
Gradient descent for multiple variables

Feature scale
	mean normalize data to converge faster (do not apply to inserted $ x_{0} $ that equals 1 for example). Adjust input values as shown in this formula.
	\begin{equation}
	x_{i} := \frac{x_{i}-\mu_{i}}{s_{i}}
	\end{equation}

	where $ \mu_{i} $ is the average of all values for feature (i) and $ s_{i} $ is the range of values ($ max(x_{i})-min(x_{i}) $) or the standard deviation of a given feature $ i $.
	get all features between -1 and 1 range or 0 and 1

Gradient descent $\mathcal{O}(n^{2})$
	\begin{equation}
	\theta_{j} := \theta_{j} - \alpha \frac{\partial}{\partial \theta_{j}}J(\theta)
	\end{equation}
	works well when n is large

Learning rate
	how to choose: look graph min J vs No. of iterations. It should decrease at every iteration.

Polynomial regression
	Create new features to fit a polynomial regression to a linear regression.
	E.g.

	\begin{equation}
	x_{0} = (feature)
	\end{equation}
	\begin{equation}
	x_{1} = (feature)^{2}
	\end{equation}

Analytic solution (faster convergence)
	The value of $ \theta = (X^{T}X)^{-1}X^{T}y $ (normal equation) gives the optimal value of $\theta$ that minimizes $ J(\theta) $
	Don't need to iterate nor choose $\alpha$.
	Compute the inverse costs a lot $\mathcal{O}(n^{3})$. So it is preferably to use if n is small over the iterative method.
	Noninvertibility: pinv -> pseudo inverse: calculates the value of the inverse even if it is non inversible.
